### 2020-10-16 priority-cp.tex
give space to results

Our translation satisfies operational correspondence. We link our translations, and show that $\tm{\cpgvM{P}}$ \emph{must} reduce to $\tm{\cpgvC{P}}$, \ie $\tm{\cpgvC{\cdot}}$ is equivalent to translating with $\tm{\cpgvM{\cdot}}$ and performing several reduction steps. We use this fact to prove operational correspondence. The details are in~\cref{prf:lem-pcp-to-pgv-cpgvM-to-cpgvC,prf:thm-pcp-to-pgv-operational-correspondence-completeness,prf:thm-pcp-to-pgv-operational-correspondence-soundness}:
\begin{compacttheorems}
  \begin{restatablelemma}{lempcptopgvcpgvMtocpgvC}
    \label{lem:pcp-to-pgv-cpgvM-to-cpgvC}
    For any $\pcp{\tm{P}}$, either:
    \begin{itemize}
    \item $\pgv{\tm{\child\;\cpgvM{P}}=\tm{\cpgvC{P}}}$; or
    \item   $\pgv{\tm{\child\;\cpgvM{P}}\cred^+\tm{\cpgvC{P}}}$, and for any $\pgv{\tm{\conf{C}}}$, if $\pgv{\tm{\child\;\cpgvM{P}}\cred\tm{\conf{C}}}$, then $\pgv{\tm{\conf{C}}\cred^\star\tm{\cpgvC{P}}}$.
    \end{itemize}
  \end{restatablelemma}
  \begin{restatabletheorem}{thmpcptopgvoperationalcorrespondencesoundness}%
    [Operational Correspondence, Soundness, ${\tm{\cpgvC{\cdot}}}$]
    \label{thm:pcp-to-pgv-operational-correspondence-soundness}
    \hfill\\%newline before theorem statement
    If $\pcp{\seq{P}{\ty{\Gamma}}}$ and $\pgv{\tm{\cpgvC{P}}\cred\tm{\conf{C}}}$, there exists a $\tm{Q}$ such that $\pcp{\tm{P}\red^+\tm{Q}}$ and $\pgv{\tm{\conf{C}}\cred^\star\tm{\cpgvC{Q}}}$
  \end{restatabletheorem}
  % \begin{proof}
  %   By induction on the derivation of $\pgv{\tm{\cpgvC{P}}\cred\tm{\conf{C}}}$.\simon{Surprising that you can get it by the derivation of the reduction relation---normally, 'soundness' would be proved by shunting into a canonical form and then proceeding by induction the structure of the term / induction on typing derivations.}
  %   Details in \cref{prf:thm-pcp-to-pgv-operational-correspondence-soundness}.
  % \end{proof}
\end{compacttheorems}
\begin{restatabletheorem}{thmpcptopgvoperationalcorrespondencecompleteness}%
  [Operational Correspondence, Completeness, ${\tm{\cpgvC{\cdot}}}$]
  \label{thm:pcp-to-pgv-operational-correspondence-completeness}
  \hfill\\%newline before theorem statement
  If $\pcp{\seq{P}{\ty{\Gamma}}}$ and $\pcp{\tm{P}\red\tm{Q}}$,
  then $\pgv{\tm{\cpgvC{P}}\cred^+\tm{\cpgvC{Q}}}$. Details in~\cref{prf:lem-pcp-to-pgv-cpgvM-to-cpgvC}.
\end{restatabletheorem}
% \begin{proof}
%   By induction on the derivation of $\pcp{\tm{P}\red\tm{Q}}$. We apply \cref{lem:pcp-to-pgv-cpgvM-to-cpgvC} for the cases in which the translation switches from $\tm{\cpgvC{\cdot}}$ to $\tm{\cpgvM{\cdot}}$, \ie under actions. We apply \cref{lem:pcp-to-pgv-confs-operational-correspondence-equiv} for \LabTirName{E-LiftSC}. Details in \cref{prf:thm-pcp-to-pgv-operational-correspondence-completeness}.
% \end{proof}
\end{document}

>>>>

Our translation satisfies soundness and completeness of operational correspondence. We link ${\tm{\cpgvM{\cdot}}}$ and ${\tm{\cpgvC{\cdot}}}$ and show that $\tm{\cpgvM{P}}$ \emph{must} reduce to $\tm{\cpgvC{P}}$, \ie $\tm{\cpgvC{\cdot}}$ is equivalent to translating with $\tm{\cpgvM{\cdot}}$ and performing several reduction steps. We use this fact to prove the results below. The details are in~\cref{prf:lem-pcp-to-pgv-cpgvM-to-cpgvC,prf:thm-pcp-to-pgv-operational-correspondence-completeness,prf:thm-pcp-to-pgv-operational-correspondence-soundness}:
  \begin{restatablelemma}{lempcptopgvcpgvMtocpgvC}
    \label{lem:pcp-to-pgv-cpgvM-to-cpgvC}
    For any $\pcp{\tm{P}}$, either:
    \begin{itemize}
    \item $\pgv{\tm{\child\;\cpgvM{P}}=\tm{\cpgvC{P}}}$; or
    \item   $\pgv{\tm{\child\;\cpgvM{P}}\cred^+\tm{\cpgvC{P}}}$, and for any $\pgv{\tm{\conf{C}}}$, if $\pgv{\tm{\child\;\cpgvM{P}}\cred\tm{\conf{C}}}$, then $\pgv{\tm{\conf{C}}\cred^\star\tm{\cpgvC{P}}}$.
    \end{itemize}
  \end{restatablelemma}
  \begin{restatabletheorem}{thmpcptopgvoperationalcorrespondencesoundness}%
    [Operational Correspondence, Soundness, ${\tm{\cpgvC{\cdot}}}$]
    \label{thm:pcp-to-pgv-operational-correspondence-soundness}
    \hfill\\%newline before theorem statement
    If $\pcp{\seq{P}{\ty{\Gamma}}}$ and $\pgv{\tm{\cpgvC{P}}\cred\tm{\conf{C}}}$, there exists a $\tm{Q}$ such that $\pcp{\tm{P}\red^+\tm{Q}}$ and $\pgv{\tm{\conf{C}}\cred^\star\tm{\cpgvC{Q}}}$
  \end{restatabletheorem}
  % \begin{proof}
  %   By induction on the derivation of $\pgv{\tm{\cpgvC{P}}\cred\tm{\conf{C}}}$.\simon{Surprising that you can get it by the derivation of the reduction relation---normally, 'soundness' would be proved by shunting into a canonical form and then proceeding by induction the structure of the term / induction on typing derivations.}
  %   Details in \cref{prf:thm-pcp-to-pgv-operational-correspondence-soundness}.
  % \end{proof}
\begin{restatabletheorem}{thmpcptopgvoperationalcorrespondencecompleteness}%
  [Operational Correspondence, Completeness, ${\tm{\cpgvC{\cdot}}}$]
  \label{thm:pcp-to-pgv-operational-correspondence-completeness}
  \hfill\\%newline before theorem statement
  If $\pcp{\seq{P}{\ty{\Gamma}}}$ and $\pcp{\tm{P}\red\tm{Q}}$,
  then $\pgv{\tm{\cpgvC{P}}\cred^+\tm{\cpgvC{Q}}}$.
\end{restatabletheorem}
% \begin{proof}
%   By induction on the derivation of $\pcp{\tm{P}\red\tm{Q}}$. We apply \cref{lem:pcp-to-pgv-cpgvM-to-cpgvC} for the cases in which the translation switches from $\tm{\cpgvC{\cdot}}$ to $\tm{\cpgvM{\cdot}}$, \ie under actions. We apply \cref{lem:pcp-to-pgv-confs-operational-correspondence-equiv} for \LabTirName{E-LiftSC}. Details in \cref{prf:thm-pcp-to-pgv-operational-correspondence-completeness}.
% \end{proof}
\end{document}
